Application of Machine Learning to Increase the Efficiency of the Global Search Algorithm for Solving Multicriterial Problems\thanks{This research was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2023-11-02 2023/NUMTA/Full paper/NUMTA_2023_MCO.tex
add letter sign

@@

\begin{document}
%
\title{Application of Machine Learning to Increase the Efficiency of the Global Search Algorithm for Solving Multicriterial Problems\thanks{This research was supported by the Russian Science Foundation, project No. 21-11-00204.}}
%
\titlerunning{Global Search Algorithm for Solving Multicriterial Problems}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Konstantin Barkalov\orcidID{0000-0001-5273-2471} \and
Vladimir Grishagin\orcidID{0000-0002-2884-3670} \and
Evgeny Kozinov\orcidID{0000-0001-6776-0096}}
%
\authorrunning{K. Barkalov, V. Grishagin and E. Kozinov}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \email{\{konstantin.barkalov,evgeny.kozinov\}@itmm.unn.ru}, \email{vagris@unn.ru}}

>>>>

\usepackage[misc,geometry]{ifsym}

@@

\begin{document}
%
\title{Application of Machine Learning to Increase the Efficiency of the Global Search Algorithm for Solving Multicriterial Problems\thanks{This research was supported by the Russian Science Foundation, project No. 21-11-00204.}}
%
\titlerunning{Global Search Algorithm for Solving Multicriterial Problems}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Konstantin Barkalov \Letter \orcidID{0000-0001-5273-2471} \and
Vladimir Grishagin\orcidID{0000-0002-2884-3670} \and
Evgeny Kozinov\orcidID{0000-0001-6776-0096}}
%
\authorrunning{K. Barkalov, V. Grishagin and E. Kozinov}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \email{\{konstantin.barkalov,evgeny.kozinov\}@itmm.unn.ru}, \email{vagris@unn.ru}}
